A Spiking Independent Accumulator Model for Winner-Take-All Networks \todo{I put 'networks', but am not sure that's the right word, but it seems some word needs to go there... 'computations', 'decisions'? WTA is usually an adjective}

### 2017-01-30 doc/paper/paper.tex
Remove todo.
Make subfigures match col width.

\subsubsection{Principle 1: Representation}
We define the representation of a scalar value $x(t)$ by an encoding and decoding with respect to some population of neurons.
The encoding of $x(t)$ into a spike train $a_i(t)$ for neuron $i$ is given by:
\begin{equation}
    a_i(t) = G_i\left[\alpha_i e_i x(t) + J_i^{\mathrm{bias}}\right] ,
\end{equation}
where $\alpha_i$ is a gain factor, $e_i$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$, and set the encoders to one.
Decoding weights $d_i$ are then used to approximate the represented value $\hat x(t)$ from the activity of the population of neurons by:
\begin{equation}
    \hat x(t) = \sum_i d_i \left[(a_i * h)(t)\right] ,
\end{equation}
where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(t/\tau_{\mathrm{s}})$ is an exponentially decaying synaptic filter with time-constant $\tau_{\mathrm{s}}$, and $\ast$ is the convolution operator.
The decoding weights are obtained by least-squares optimization of the error $E_x = \abs{x - \hat{x}}$.
\todo{do you actually use absolute value?  should these be double bars?}
For the transmission of a value from one population to another, the connection weights are given by:
\begin{equation}
    W_{ij} = \alpha_j e_j d_i \text{.}
\end{equation}

@@

As shown in Fig.~\ref{fig:time}a, the time required to reach a decision in the LCA network depends mostly on the size of inputs and target separation.
We averaged over the different noise conditions because the noise influence on the timing was minor.
In the IA network the largest input is the most important factor (dashed vs.\ solid lines in Fig.~\ref{fig:time}b).
Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time given a value of $\tau_1$ that achieves the same fraction of correct responses as the LCA network.
There is also a slight influence of target separation and input noise, with an interaction of these two parameters (solid lines in Fig.~\ref{fig:time}).
\begin{figure*}[t]
    \centering
    \includegraphics{figures/time}
    \caption{
        \todo{Can you make it so that the left / right subfigures are aligned with the left / right columns? Currently the left subfigure stretches over the center dividing line.}
        (Left) Mean decision times for the LCA network.
        Shown data is averaged across all noise levels, since noise had minimal effect on decision times.
        (Right) Mean decision times for the IA network with input magnitude $u = 0.2$ (solid) and $u = 1$ (dashed).
        Error bars denote bootstrapped 95\% confidence intervals.
    }\label{fig:time}
\end{figure*}

>>>>

\subsubsection{Principle 1: Representation}
We define the representation of a scalar value $x(t)$ by an encoding and decoding with respect to some population of neurons.
The encoding of $x(t)$ into a spike train $a_i(t)$ for neuron $i$ is given by:
\begin{equation}
    a_i(t) = G_i\left[\alpha_i e_i x(t) + J_i^{\mathrm{bias}}\right] ,
\end{equation}
where $\alpha_i$ is a gain factor, $e_i$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$, and set the encoders to one.
Decoding weights $d_i$ are then used to approximate the represented value $\hat x(t)$ from the activity of the population of neurons by:
\begin{equation}
    \hat x(t) = \sum_i d_i \left[(a_i * h)(t)\right] ,
\end{equation}
where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(t/\tau_{\mathrm{s}})$ is an exponentially decaying synaptic filter with time-constant $\tau_{\mathrm{s}}$, and $\ast$ is the convolution operator.
The decoding weights are obtained by least-squares optimization of the error $E_x = \abs{x - \hat{x}}$.
For the transmission of a value from one population to another, the connection weights are given by:
\begin{equation}
    W_{ij} = \alpha_j e_j d_i \text{.}
\end{equation}

@@

As shown in Fig.~\ref{fig:time}a, the time required to reach a decision in the LCA network depends mostly on the size of inputs and target separation.
We averaged over the different noise conditions because the noise influence on the timing was minor.
In the IA network the largest input is the most important factor (dashed vs.\ solid lines in Fig.~\ref{fig:time}b).
Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time given a value of $\tau_1$ that achieves the same fraction of correct responses as the LCA network.
There is also a slight influence of target separation and input noise, with an interaction of these two parameters (solid lines in Fig.~\ref{fig:time}).
\begin{figure*}[t]
    \includegraphics{figures/time1}
    \hfill
    \includegraphics{figures/time2}
    \caption{
        (Left) Mean decision times for the LCA network.
        Shown data is averaged across all noise levels, since noise had minimal effect on decision times.
        (Right) Mean decision times for the IA network with input magnitude $u = 0.2$ (solid) and $u = 1$ (dashed).
        Error bars denote bootstrapped 95\% confidence intervals.
    }\label{fig:time}
\end{figure*}
